4d $\cN=1$

### 2019-11-12 4dsusy.tex

\subsection{Theories of matter}
To define the chiral multiplet we fix a complex vector space $R$, and denote the natural pairing between $R$ and $R^*$ by $\<-,-\>_R$. 
The spinorial pairing $\<-,-\> : S_\pm \otimes S_\pm \to \CC$ induces a pairing between $S_\pm \otimes R$ and $S_{\pm} \otimes R^*$ that we also denote by $\<-,-\>_R$.

The field content for the 4-dimensional chiral multiplet with values in a complex vector space $R$ is:
\begin{itemize}
\item a pair of scalars $\phi \in C^\infty(\RR^4 ; R)$ and $\Bar{\phi} \in C^\infty(\RR^4 ; R^*)$.
\item a left Weyl spinor $\psi_+ \in C^\infty(\RR^4 ; R \otimes S_+)$ and a right Weyl spinor $\psi_- \in C^\infty(\RR^4 ; R^* \otimes S_-)$.
\end{itemize}

@@

The BRST action is
\[
S (\phi, \Bar{\phi}, \psi_\pm) = \int_{\RR^4} \d^4 x \; \<\d \phi , * \d \Bar{\phi}\>_R + \int \d^4 x \; \<\psi_+ , \sd \dd \psi_-\>_R .
\]

@@

In some dimensions $n \leq 6$ there exists {\em matter} representations of supersymmetry.

\begin{itemize}
\item Dimension $n=4$, the chiral multiplet.
\item Dimension $n=6$, hyper multiplet. 
\end{itemize}

@@

The action of the odd part of the $4d$ $\cN=1$ supersymmetry algebra on the $4$-dimensional matter theory is encoded by the following linear and quadratic functionals 
\begin{align*}
I^{(1)}(Q) & = \int \<\phi^* + \Bar{\phi}^*, (Q, \psi_+ + \psi_-)\>_R + \<\psi_+^* + \psi_-^*, \rho(\d \phi + \d \Bar{\phi})Q \>_R \\
I^{(2)}  (Q_1 \otimes Q_2) & = \int \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\psi_+^* + \psi_-^*, \psi_+^*+\psi_-^*)) - \frac{1}{2}(Q_1, \psi_+^* + \psi_-^*)(Q_2, \psi_+^*+\psi_-^*)
\end{align*}
for $Q, Q_1, Q_2 \in S_+ \oplus S_-$

\begin{thm}
The functional $\fS = S + I_{\rm Poin}^{(1)} + I^{(1)} + I^{(2)}$ with $I_{\rm Poin}$ as in Section \ref{??} satisfies the classical master equation
\[
\d_{\rm Lie} \fS + \frac{1}{2} \{\fS, \fS\} = 0 .
\]
\end{thm}

>>>>

\subsection{Theories of matter}
In this subsection, $S_+ / S_-$ denote the positive/negative irreducible spin representations of $\mf{so}(4; \CC)$. 
To define the chiral multiplet we fix a complex vector space $R$.
The spinorial pairing $(-,-) : S_\pm \otimes S_\pm \to \CC$ induces a pairing between $S_\pm \otimes R$ and $S_{\pm} \otimes R^*$ that we also denote by $(-,-)_R$.

The field content for the 4-dimensional chiral multiplet with values in a complex vector space $R$ is:
\begin{itemize}
\item a pair of scalars $\phi \in C^\infty(\RR^4 ; R)$ and $\Bar{\phi} \in C^\infty(\RR^4 ; R^*)$.
\item a positive Weyl spinor $\psi_+ \in C^\infty(\RR^4 ; R \otimes S_+)$ and a negative Weyl spinor $\psi_- \in C^\infty(\RR^4 ; R^* \otimes S_-)$.
\end{itemize}

@@

The BRST action is
\[
S (\phi, \Bar{\phi}, \psi_\pm) = - \int_{\RR^4} (\d \phi \wedge * \d \Bar{\phi})_R + \int (\psi_+ , \sd \dd \psi_-)_R .
\]

@@

In some dimensions $n \leq 6$ there exists the following {\em matter} representations of supersymmetry.

\begin{itemize}
\item Dimension $n=4$, with $\Sigma = S_+ \otimes R \oplus S_- \otimes R^*$, with $R$ a complex vector space.
This is called the $\cN=1$ chiral multiplet.
\item Dimension $n=6$, with $\Sigma = S_+ \oplus W_+$ (or $\Sigma = S_- \otimes W_-$), with $W_+$ (or $W_-$) a complex, symplectic representation. This is called the $\cN=(1,0)$ (or $\cN=(0,1)$) hyper multiplet. 
\end{itemize}

@@

In this subsection, $S_+ / S_-$ denote the positive/negative irreducible spin representations of $\mf{so}(4; \CC)$.

The action of the odd part of the $4d$ $\cN=1$ supersymmetry algebra on the $4$-dimensional matter theory is encoded by the following linear and quadratic functionals 
\begin{align*}
I^{(1)}(Q) & = \int \<\phi^*, (Q, \psi_+)\>_R + \<\Bar{\phi}^*, (Q, \psi_-)\>_R + \<\psi_+^*, \rho(\d \phi)Q \>_R +  \<\psi_-^*, \rho(\d \Bar{\phi})Q \>_R \\
I^{(2)}  (Q_1 \otimes Q_2) & = \int \frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\psi_+^*, \psi_-^*)) - \int (Q_1, \psi_+^*)(Q_2, \psi_-^*) - \int (Q_2, \psi_+^*)(Q_1, \psi_-^*) 
\end{align*}
for $Q, Q_1, Q_2 \in S_+ \oplus S_-$

\begin{thm}
The functional $\fS = S + I^{(1)} + I^{(2)}$ satisfies the classical master equation
\begin{equation}\label{CMEchiral}
\d_{\rm Lie} \fS + \frac{1}{2} \{\fS, \fS\} = 0 .
\end{equation}
\end{thm}

Before proving the theorem, we decompose the classical master equation (\ref{CMEchiral}) into the following equations:
\begin{equation}\label{CMEchiral2}
\begin{array}{rrrrrr}
\{S , I^{(1)}\} & = & 0 \\ 
\{S, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2} \{I^{(1)}, I^{(1)}\} & = & 0 \\
\d_{CE} I^{(2)} + \{I^{(1)}, I^{(2)}\} & =& 0 \\
\{I^{(2)}, I^{(2)}\} & =& 0
\end{array}
\end{equation}

The last equation is automatically satisfied since $I^{(2)}$ is independent of $\phi, \Bar{\phi}$, and $\psi_{\pm}$.

The first equation in (\ref{CMEchiral2}) states that the classical action for the chiral multiplet is supersymmetric.

\begin{lemma} 
One has $\{S, I^{(1)}\} (Q) = 0$ for all $Q \in S_+ + S_-$. 
\end{lemma}
\begin{proof}
The BV bracket involving terms in $S$ depending on $\phi,\Bar{\phi}$ is:
\begin{align*}
- \left\{\d \phi \wedge * \d \Bar{\phi} \; , \; I^{(1)} \right\}  (Q) & = \d (Q, \psi_+) \wedge * \d \Bar{\phi} + \d \phi \wedge * \d (Q_-, \psi_-) \\
& = \Gamma(\sd \dd \psi_+, Q) \wedge * \d \Bar{\phi} \pm \d \phi \wedge * \Gamma(\sd \dd \psi_-, Q_-) .
\end{align*}
The BV bracket involving terms in $S$ depending on $\psi_\pm$ is:
\begin{align*}
\left\{ (\psi_+ , \sd \dd \psi_-) \; , \; I^{(1)} \right\} (Q) & = (\rho(\d \phi) Q, \sd \dd \psi_-) + (\psi_+, \sd \dd (\rho(\d \Bar{\phi}) Q)) \\ & =  (\rho(\d \phi) Q, \sd \dd \psi_-) - (\sd \dd \psi_+, (\rho(\d \Bar{\phi}) Q) \\ & = \d \phi \wedge * \Gamma(\sd \dd \psi_-, Q) - \d \Bar{\phi} \wedge * \Gamma(\sd \dd \psi_+, Q)
\end{align*}
Adding the two terms up, we see that $\{S,I^{(1)}\}(Q) = 0$, as desired. 
\end{proof}

Next, we move on to the second equation in (\ref{CMEchiral2}).

\begin{lemma} 
One has
\begin{equation}\label{CMEchiral3}
\{S, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2} \{I^{(1)}, I^{(1)}\} = 0 .
\end{equation}
\end{lemma}
\begin{proof}
Evaluating the equation (\ref{CMEchiral3}) on $v_1,v_2 \mf{iso}(V)$ reduces to the claim that (??) defines a strict Lie action. 
Evaluating on $v \in \mf{iso}(V)$ and $Q \in S_+ \oplus S_-$, the claim reduces to the fact that $I^{(1)}$ is Poincar\'{e} invariant.
So, the only nontrivial term to check is the evaluation on $Q_1,Q_2 \in S_+ \oplus S_-$.

The individual terms are:
\begin{align*}
\{I^{(1)}, I^{(1)}\}(Q_1, Q_2) = & - \phi^* (Q_1, \rho(\d \phi) Q_2) - \phi^* (Q_2, \rho(\d \phi)Q_1) \\ & - \Bar{\phi}^* (Q_1, \rho(\d \Bar{\phi}) Q_2) - \Bar{\phi}^* (Q_2, \rho(\d \Bar{\phi})Q_1) \\ &  -  (\psi_+^*, \rho(\d(Q_1,\psi_+))Q_2) - (\psi_+^*, \rho(\d(Q_2, \psi_+)) Q_1) \\ & - (\psi_-^*, \rho(\d(Q_1, \psi_-)) Q_2) - (\psi_-^*, \rho(\d(Q_2, \psi_-))Q_1) 
\end{align*}

\begin{align*}
(\d_{CE}I^{(1)})(Q_1,Q_2) = & - \phi^* L_{\Gamma(Q_1,Q_2)} (\phi) - \Bar{\phi}^* L_{\Gamma(Q_1,Q_2)} \Bar{\phi} \\ &  - (\psi_+^* , \Gamma(Q_1,Q_2) . \psi_+) - (\psi_-^*, \Gamma(Q_1,Q_2) . \psi_-)
\end{align*}

and
\begin{align*}
\{S, I^{(2)}(Q_1,Q_2)\} = & 
\end{align*}

We first collect all terms in Equation (\ref{CMEchiral3}) proportional to $\phi^*$:
\[
- \frac{1}{2} (Q_1, \rho(\d\phi) Q_2) - \frac{1}{2} (Q_2, \rho(\d \phi) Q_1) - L_{\Gamma(Q_1,Q_2)} \phi .
\]
By Proposition \ref{??}
\brian{ $v \wedge \Gamma(Q_1, Q_2) = (Q_1 , \rho(v) Q_2)$} we observe that the first two terms cancel with the third term. 
Similarly, all terms proportional to $\Bar{\phi}^*$ also vanish.

Next, we collect all terms in Equation (\ref{CMEchiral3}) proportional to $\psi_+^*$:
\begin{align*}
& - \frac{1}{2} \rho(\d(Q_1,\psi_+))Q_2 - \frac{1}{2} \rho(\d(Q_2, \psi_+)) Q_1 - \Gamma(Q_1,Q_2) . \psi_+
\\ 
& \pm \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi_+ \mp \frac{1}{2} (Q_2, \sd \dd \psi_+)Q_1 \mp \frac{1}{2} (Q_1, \sd \dd \psi_+)Q_2
\end{align*}

\end{proof}

\begin{lemma}
\[\{I^{(1)}, I^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
for every $Q_1, Q_2, Q_3\in S_+ \oplus S_-$.
\end{lemma}
\begin{proof}
We have
\begin{align*}
\{I^{(1)}(Q_1), I^{(2)}(Q_2, Q_3)\} = 
\end{align*}

$\{I^{(1)}, I^{(2)}\}$ is obtained by cyclically symmetrizing the above expression. By Proposition \ref{prop:3psi} the cyclic symmetrization of the term with $c^*$ is zero. The Clifford relation implies that
%\begin{align*}
%\frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(A^*) Q_1, \lambda^*)) &= -\frac{1}{2}(\Gamma(Q_2, Q_3), \Gamma(\rho(A^*)\lambda^*, Q_1)) + (\Gamma(Q_2, Q_3), A^*) (Q_1, \lambda^*) \\
%&= -\frac{1}{2}(\rho(\Gamma(Q_2, Q_3)) Q_1, \rho(A^*)\lambda^*) + (\Gamma(Q_2, Q_3), A^*) (Q_1, \lambda^*).
%\end{align*}
%Therefore, again using Proposition \ref{prop:3psi} we see that the cyclic symmetrization of the terms with $A^*$ vanishes.
\end{proof}
